Adapting the Chumbley Score to Bullet Striations

### 2018-04-25 presentation/presentation.Rmd
some additions

@@

- Number is highly dependent on the comparison window sizes
- Correlated to the ground truth, 
- \textbf{Higher for known same-sourced lands (CS1)} than for known different sourced lands. 
- \textbf{CS1} fails to conduct a test about 8 to 13 % of the time for \textbf{known same-source lands}, and 2 to 6% of the time for \textbf{known different source lands}.
- Number for CS1 always higher than the corresponding theoretical number of failed tests.
- Using CS2, the case with \textbf{largest} # of failed tests is still \textbf{lower} than the case where CS1 gives the \textbf{lowest} # of failed tests
- Even for high coarseness, CS2 will have lower number of failed tests than CS1, Making it more robust.
- CS2 performs better for \textbf{both} same and different-sources
- Solves a \textbf{critical issue} of CS1 known same-source matching, by having a \textbf{negligible number of Known same-source failed tests}

>>>>

\begin{figure}[hbtp]
\centering
\includegraphics[width=0.9\textwidth]{imgs/failed-tests.png}
\caption{\label{type2}  Percent of failed land-to-land comparisons for $w_o$ = 120 and coarseness $c$ = 0.25}
\end{figure}

@@

- With an increase in the $w_v$ higher percent of tests fail under both CS1 and CS2
- Number is highly dependent on the comparison window sizes
- Correlated to the ground truth, 
- \textbf{Higher for known same-sourced lands (CS1)} than for known different sourced lands. 
- \textbf{CS1} fails to conduct a test about 8 to 13 % of the time for \textbf{known same-source lands}, and 2 to 6% of the time for \textbf{known different source lands}.
- Number for CS1 always higher than the corresponding theoretical number of failed tests.
- Using CS2, the case with \textbf{largest} # of failed tests is still \textbf{lower} than the case where CS1 gives the \textbf{lowest} # of failed tests
- Even for high coarseness, CS2 will have lower number of failed tests than CS1, Making it more robust.
- CS2 performs better for \textbf{both} same and different-sources
- Solves a \textbf{critical issue} of CS1 known same-source matching, by having a \textbf{negligible} number of Known same-source failed tests
